Quick Research Review

### 2018-11-18 presentations/Su_DL_110618/Su_DL_110618.tex
reorg presentations dir

        \item Two hypotheses:
            \begin{itemize}
                \item Damping layer is causing mean flow to begin building up
                    like Daniel said; how can we fix? Seems like low $k_z$ modes
                    (which have higher $v_{ph}$).

                \item Further growth/propagation is critical layer absorption?
                    Eventual reflection might build up when shear flow is too
                    steep $\mathrm{Ri} \gtrsim 1/2$ or WKB breaks down
                    $\pd{k_z}{z} \sim \frac{k_z}{\lambda_z}$.
            \end{itemize}
    \end{itemize}
\end{frame}

>>>>

        \item Tried masking nonlinear terms near damping zones,
            \lstinline{nl3_lowres_test.mp4}. Still mean flow interaction!
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Numerical Simulations, No Shear}
    \framesubtitle{Hypotheses}
    \begin{itemize}
        \item Damping layer is causing mean flow to begin building up
            like Daniel said; is removing nonlinear terms near damping layer a
            good idea?

        \item Further growth/propagation is critical layer absorption?
            Eventual reflection might build up when shear flow is too
            steep $\mathrm{Ri} \gtrsim 1/2$ or WKB breaks down
            $\pd{k_z}{z} \sim \frac{k_z}{\lambda_z}$.

            The sign of the flow is
            wrong though, $\sim -\frac{1}{c_{gz}}\ev*{u_xu_z}_x$!
    \end{itemize}
\end{frame}
